A data-driven, pixel-level model to improve the precision of \Kepler\ photometry

### 2013-10-23 documents/plm.tex
plm pixels

Once we have obtained the $a_{mnm'}$ parameters corresponding to a particular data point $I_{mn}$,
  we can make a \emph{prediction} $I^{\ast}_{mnn}$ for the intensity at that pixel.
By construction of our objective function, this is truly a prediction,
  in the sense that the optimization (or solve) that produced the parameters
  (and thus the prediction)
  did not make use of $I_{mn}$ itself,
  or even any of the pixel values that are nearby in angle or time
  (as described above).
In addition to the predicted pixel value $I^{\ast}_{mnn}$,
  we can also construct a \emph{residual} $\Delta_{mn}$ (data minus prediction),
  defined by
\begin{eqnarray}
\Delta_{mn} &\equiv& I_{mn} - I^{\ast}_{mnn}
\quad .
\end{eqnarray}

\todo{HOGG: We construct the predicted pixels and the \name\ pixels how?}

@@

>>>>

Once we have obtained the $a_{mnm'}$ parameters corresponding to a particular data point $I_{mn}$,
  we can make a \emph{prediction} $I^{\ast}_{mnn}$ for the intensity at that pixel.
By construction of our objective function, this is truly a prediction,
  in the sense that the optimization (or solve) that produced the parameters
  (and thus the prediction)
  did not make use of $I_{mn}$ itself,
  or even any of the pixel values that are nearby in angle or time
  (as described above).
In addition to the predicted pixel value $I^{\ast}_{mnn}$,
  we can also construct a \emph{residual} $\delta_{mn}$ (data minus prediction),
  defined by
\begin{eqnarray}
\delta_{mn} &\equiv& I_{mn} - I^{\ast}_{mnn}
\quad .
\end{eqnarray}

In some sense, it is this residual that contains the exoplanet transit signals we seek.
That is, a transit creates a negative residual away from the prediction.
So far, however, the model is a model of \emph{pixels},
  and we need to obtain from this model \emph{photometric measurements} of stars.
In order to construct stellar photometry measurements out of the residual pixels $\delta_{mn}$,
  we add into each pixel residual $\delta_{mn}$ the \emph{mean predicted intensity} $\bar{I}^{\ast}_m$
\begin{eqnarray}
\bar{I}^{\ast}_m &=& \frac{1}{N_m}\,\sum_n I^{\ast}_{mnn}
\quad ,
\end{eqnarray}
where $N_m$ is the number of time steps in the quarter,
  and the sum is over those time steps.
We construct what we will call ``the \name\ photometry''
  from what we will call ``the \name\ pixels'' $J_{mn}$,
  which are the residuals plus the mean, or
\begin{eqnarray}
J_mn &=& \delta_{mn} + \bar{I}^{\ast}_m
\quad .
\end{eqnarray}
That is, \todo{WTF}

@@

\todo{Hogg \& DFM:  Why does the above make no fucking sense?}
